Bacterial Microbiome and Obesity Meta-analysis Supplemental

### 2016-03-31 microbiomeAndobesitySupplemental.Rmd
update code for pdf

```{r Figure_S4, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}

@@

# Generate Funnel Plots for supplemental
par(mfrow=c(1,2))
funnel(res, main="A")
funnel(res2, main="B")
```

@@

```{r Figure_S5, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}

@@

```{r Figure_S6, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}

@@

```{r Figure_S7, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}

@@

```{r Figure_S8, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}

@@

```{r Figure_S9, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}

@@

```{r Figure_S10, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}

>>>>

```{r Figure_S4, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

# Generate Funnel Plots for supplemental
par(mfrow=c(1,2))
funnel(res, main="A")
funnel(res2, main="B")

@@

```{r Figure_S5, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S6, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S7, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S8, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S9, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S10, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}
